---
title: "Comparing Petal Length by Species"
author: "Kira"
data: "2020-01-17"
output: html_document
---

By following this code, you will be able to compare species based on petal length in boxed plot form. 

First make sure your working directory is in the right location. 
```{r}
getwd() 
```
If it is not, set it using a path to your working directory. If your working directory is correct, skip this step.
```{r}
# setwd() 
```

The Iris data set is built in, so you can jump right into renaming your iris variables, in this case petal length and species name.
```{r}
petalL <- iris$Petal.Length
species <- iris$Species
```

Next we want to group our variable, petal length, into the three major categories presented as species.
```{r}
unique(species)
pl.setosa <- petalL[species=="setosa"]
pl.virginica <- petalL[species=="virginica"]
pl.versicolor <- petalL[species=="versicolor"]
```


This creates a boxplot out of the three grouped variables we named above. We can now see in box plot form how the species compare/contrast in petal length. We have also given each one a seperate color, and named the two axes. Because the x axis is only labeled as species, it is important to note the different between them. This creates a legend titled Speceis, names the species, and pairs them with the color of their box. It also tells R where to place the legend, in the bottom right. 
```{r}
boxplot(pl.setosa, pl.virginica, pl.versicolor, col=c("red", "green", "blue"), xlab="Species", ylab="Petal Length")
legend("bottomright", inset=.02, title="Species", legend=c("Setosa", "Virginica", "Versicolor"), fill=c("red", "green", "blue"), horiz=TRUE)
```
