---
title: "Ethan's Iris Analysis in RMarkdown"
author: "Ethan Hill"
date: "2020-01-20"
output: html_document
---

Hello! Here are the plots and the code for the plots I have generated with the Iris dataset. I have also gone ahead and included the workflow I used to get the final plots...


It is always a good habit to set your working directory:

```{r}
setwd("C:/Users/hille/Documents/Rbootcamp_S2020/Iris-repo/")
```


Next, I've scrambled the iris dataset (gotta make it harder) and stored the scrambled data into the object called mix and seperate each column as a vector:

```{r}
oo <- sample(x=1:150, 150, replace=FALSE)
mix <- iris[oo,]

species <- mix$Species
petalL <- mix$Petal.Length
petalW <- mix$Petal.Width
sepalL <- mix$Sepal.Length
sepalW <- mix$Sepal.Width
```


Now, I can take the species vector and assign each species its own unique color based on logical operations:

```{r}
species
color <- rep("red", 150)
species == "setosa"
color[species == "setosa"] <- "purple"
color
color[species == "versicolor"] <- "blue"
color
color[species == "virginica"] <- "orange"
color
```

Cool, Now we can start doing some real analyses. 
I have have made a best fit line of regression for Sepal Width as a function of Petal Length and have displayed the output stats:

```{r}
sepalW.lm <- lm(sepalW ~ petalL)
sepalW.lm
```


This is a scatter plot for "Petal Length vs Petal Width" with a line of best fit.
```{r}
plot(petalL, sepalW, col=color, cex=1.5, pch=19, xlab="Petal Length", ylab="Sepal Width")
abline(sepalW.lm, col="black")
legend('top', legend = levels(species), col = c("purple", "blue", "orange"), cex = .8, pch = 19)
```

As we can see from the graph above, the "general" trend is that as petal length increases, the sepal width decreases.

BUT WAIT THERE'S MORE!!!!


We can also index the iris dataset by species and make a regression line for Sepal Width as a function of Petal Length FOR EACH SPECIES and we can ALSO calcuate error for the linear regression FOR EACH SPECIES:
```{r]
setosa <- mix[mix$Species == "setosa",]
setosa
setosaPLvsSW.lm <- lm(setosa$Sepal.Width ~ setosa$Petal.Length)
setosaPLvsSW.lm

versicolor <- mix[mix$Species == "versicolor",]
versicolor
versicolorPLvsSW.lm <- lm(versicolor$Sepal.Width ~ versicolor$Petal.Length)
versicolorPLvsSW.lm


virginica <- mix[mix$Species == "virginica",]
virginica
virginicaPLvsSW.lm <- lm(virginica$Sepal.Width ~ virginica$Petal.Length)
virginicaPLvsSW.lm
```

THEN WE CAN PLOT THE DATA AGAIN WITH EACH SPECIES HAVING THEIR OWN LINE OF REGRESSION:
```{r}
plot(petalL, sepalW, col=color, cex=1.5, pch=19, xlab="Petal Length", ylab="Sepal Width")
abline(setosaPLvsSW.lm, col="purple")
abline(versicolorPLvsSW.lm, col="blue")
abline(virginicaPLvsSW.lm, col="orange")
legend('topright', legend = levels(species), col = c("purple", "blue", "orange"), cex = 1, pch = 19)
```

What we can see from THIS plot is that, within species, as petal length increases, sepal width ALSO increases. WOW, who would have thought.

And this will conclude my simple anaylsis of the iris dataset!

